---
title: "Random forest analysis"
output:
  html_document:
    df_print: paged
    toc: TRUE
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"), fig.width = 10, fig.height = 4)
options(knitr.table.format = "html")
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(viridis)
library(Replicate)
library(metafor)
library(esc)
library(here)
library(brms)
library(rstan)
library(googledrive)
library(glmnet)
library(tidybayes)
library(ggstance)
library("lattice")
library(reshape2)
library(ggrepel)
library(ggthemes)
library(knitr)
library(cowplot)
library(ggtext)
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
library(ggtext)
library(ggridges)

theme_set(theme_bw())

images <- "images"

prediction_loc <- "model_predictions"
dat_loc <- "other_data"

human <- read_csv(here(dat_loc, "human_data.csv")) # tg-matcher data

source(here("analyses/helper.R"))

```

```{r}
rf_mod <- read_csv(here(prediction_loc, "random_forest_stimulus_predictions.csv")) |> rename(prediction = predicted, label = tangram)

```

# Model Accuracy by round and condition 

It increases over repNum, which is ... interesting?!

```{r}
plot_accuracy(rf_mod, "random forest")
```

## Model accuracy by tangram

Above chance at everything! No longer hates the ice skater. 

```{r}
plot_accuracy_tangram(rf_mod, "random forest")
```

## Accuracy as funct of number of words

TODO needs work

could try ridge plots for by round number 

want density

and want to debate functional form


```{r}

rf_mod |>
  left_join(combined_chat) |>
  mutate(correct = ifelse(prediction == label, 1, 0)) |>
  ggplot(aes(x = words, y = as.factor(repNum), fill = as.factor(repNum))) +
  geom_density_ridges() +
  scale_fill_viridis(discrete = T) +
  labs(y="Round")+
  theme(legend.position = "none")

plot_accuracy_length(rf_mod, "Random forest")
```

## Confusion Matrix

versus truth 

```{r}
do_confusion(rf_mod, "random_forest")
```



# Comparison with all tg-matcher
Compare the random forest  with human results 


```{r, message=F}
plot_model_naive_human(rf_mod, "random forest")
```


## Individual correlation

Item level correlation between correct and wrong responses (model & per-human response)

Not sure how to look for correlated error patterns...

```{r}

plot_individual_corr(rf_mod, "random forest")
```
